---
title: "wk1_day5_quarto_stuff"
author: "Joshua Paul Cohen"
format: html
execute: 
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---

```{r}
# were gonna filter out all the warnings and shit from the quarto render
#| warning: false
#| message: false

# load libraries
library(tidyverse)
library(ggplot2)

```

## running `head()`, `tail()`, `dim()`, and `dplyr::insert_table` on table "starwars"

```{r}
#summry stats
head(starwars, n = 10)
tail(starwars)
dim(starwars)
dplyr::starwars
```

## now?
### create scatterplot of character `mass` on y axis and `height` on x
### update the color of the points so that color changes based on the value of `mass`
```{r}
# turning off warnings and code output
#| echo: false

# ploting
ggplot(data = starwars, aes(x = height, y = mass, color = mass, size = 3)) + geom_point() + labs(x = "Height (cm)", y = "Mass (kg)", title = "mewhen")
```

## next
### make histogram of character heights
### update the fill color `fill` to purple and the outside border line `color` of each histogram bin to orange
### update axis labels
### update eyour code chunck options so that only your code and output graph appear in the rendered doc

```{r}
#| fig-cap: "figure caption here"
#| fig-alt: "alt caption"
# alt captions are an accessability feature
ggplot(data = starwars, aes(x = height)) + geom_histogram(fill = "purple", color = "orange") + labs(x = "height cm", y = "frequency")
```

```{r}
# getting the mean of starwars height
# but this one should fetch an NA
# this is because there's NA's in the dataset
mean(starwars$height)
# instead we....
# we added round to round output
sw_height_mean <- round(x = mean(starwars$height, na.rm = TRUE), digits = 3)

```

mean height starwars characters is `r sw_height_mean`

phrase things "r variable" but in `backslashes` to output a variable in quarto